---
title: "SWAPBOARD"
output: 
  flexdashboard::flex_dashboard:
  #  navbar:
  #    - { title: "About", href: }
  #    - { title: "Data", href: }
    orientation: rows
  #  source_code: ""
    vertical_layout: scroll
  #  logo: Asset_2.png
runtime: shiny
---

<style>
.logo {
 size: 35%;
}
.navbar {
  background-color:orange;
  border-color:orange;
}
.navbar-brand {
color:orrange!important;
}

.navbar-nav li a:hover, .navbar-nav > .active > a {
color: orange !important;

background-color:#fff !important;
background-image: none !important;
}
</style>


```{r setup, include=FALSE}
library(flexdashboard)
library(viridis)
library(tidyverse)
library(plotly)
library(shiny)
library(scales)
library(DT)
library(writexl)
library(echarts4r)

# Gets the port # from Heroku
port <- Sys.getenv('PORT')

# Runs the app in the working directory. By default this will search for an `app.R` file or 
# a ui.R + server.R file combination
# The host of 0.0.0.0 indicates the app runs at the web server's ip address
shiny::runApp(
  appDir = getwd(),
  host = '0.0.0.0',
  port = as.numeric(port)
)
```



```{r global}
# access to data
load(url("http://s3.amazonaws.com/assets.datacamp.com/production/course_4850/datasets/movies.Rdata"))
```

Exploratory
=================================================================

Inputs {.sidebar}
-----------------------------------------------------------------------

<style>
.sidebar {
  background-color:orange;
  border-color:orange;
}
</style>

```{r}
# from https://stackoverflow.com/questions/42148177/how-can-i-build-multiple-inputs-into-my-shiny-app-with-both-updating-and-multipl

# Select variable for y-axis
selectInput(inputId = "y", 
                  label = "Y-axis:",
                  choices = c("IMDB rating"          = "imdb_rating", 
                              "IMDB number of votes" = "imdb_num_votes", 
                              "Critics score"        = "critics_score", 
                              "Audience score"       = "audience_score", 
                              "Runtime"              = "runtime"), 
                  selected = "audience_score")

# Select variable for x-axis
selectInput(inputId = "x", 
            label = "X-axis:",
            choices = c("IMDB rating"          = "imdb_rating", 
                        "IMDB number of votes" = "imdb_num_votes", 
                        "Critics score"        = "critics_score", 
                        "Audience score"       = "audience_score", 
                        "Runtime"              = "runtime"), 
            selected = "critics_score")
      
# Select variable for color
selectInput(inputId = "z", 
            label = "Color by:",
            choices = c("Title type" = "title_type", 
                        "Genre" = "genre", 
                        "MPAA rating" = "mpaa_rating", 
                        "Critics rating" = "critics_rating", 
                        "Audience rating" = "audience_rating"),
            selected = "mpaa_rating")


```


Row
-----------------------------------------------------------------------

### Highest Critics Score

```{r}
renderValueBox({ 
  critiq_score <- length(unique(movies$critics_score))
  valueBox(critiq_score, icon = "fa-commenting", color = "gray")
})
```

### Number of Movies

```{r}
renderValueBox({ 
  movies_n <- length(unique(movies$title))
  valueBox(movies_n, icon = "fa-film", color = "orange")
})
```

### Number of Production Studio

```{r}
renderValueBox({ 
  studio_n <- length(unique(movies$studio))
  valueBox(studio_n, icon = "fa-video-camera", color = "gray")
})
```

Row {data-width=400 data-height=150}
-----------------------------------------------------------------------

### Audience Satisfaction

```{r}
satisfaction <- length(unique(movies$audience_score))
gauge(satisfaction, min = 0, max = 100, symbol = '%', 
  label = "Audience Satisfaction", gaugeSectors(
  success = c(80, 100), warning = c(40, 79), danger = c(0, 39)
))
```



### Top Comment

Each component within a dashboard includes optional title, which is the text following the level 3 heading ###

Notes are any text prefaced with > after the code chunk that yields the component’s output, like



Row {data-width=400 data-height=350}
-----------------------------------------------------------------------

### Relationship between Audience Satisfaction and Critics Review

```{r}
renderPlotly({
    p <- ggplot(data = movies, aes_string(x = input$x, y = input$y,
                                     color = input$z)) +
      geom_point()
    ggplotly(p)
  })
```



### Hybrid OA licenses found (absolute)

```{r}
renderPlotly({
    p <- ggplot(data = movies, aes_string(x = input$x, y = input$y,
                                     color = input$z)) +
      geom_point()
    ggplotly(p)
  })
```


Predict
=================================================================
